RDF Constraint Types to Ensure High Data Quality

### 2015-04-29 paper/paper7/paper7.tex
evaluation
section 4

Bosch et al. identified 76 requirements to formulate RDF constraints (e.g. \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.

We developed a system to classify both RDF constraint types and RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary.
%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints of 53 distinct constraint types 
to validate tabular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}).
By applying the proposed classification system to several vocabularies to represent both metadata and data, we prove its generality \cite{BoschZapilkoWackerowEckert2015}.

@@

As vocabulary constraints are directly extractable from vocabularies and therefore ensure the syntax and semantics of vocabularies,
violations of vocabulary constraints are more severe than violations caused by simple constraints which are easily defined in addition to vocabulary constraints.
In many cases, complex constraints are also needed to express severe constraints which cannot be expressed by modeling languages.
The relation between complexity and severity shows the importance to develop constraint languages

>>>>

Bosch et al. identified 76 requirements to formulate RDF constraints (e.g. \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
We classified both RDF constraint types and RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary.
%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 246 constraints of 53 distinct constraint types on six vocabularies \cite{BoschZapilkoWackerowEckert2015}.

@@

As vocabulary constraints are directly extractable from vocabularies and therefore ensure the syntax and semantics of vocabularies,
violations of vocabulary constraints are more severe than violations caused by simple constraints which are easily defined in addition to vocabulary constraints.
In many cases, complex constraints are also needed to express severe constraints which cannot be expressed by modeling languages.
The relation between complexity and severity shows the importance to develop constraint languages which are enable to express severe complex constraints.
